Towards a Neural Co-Processor Which Restores Movement After Stroke: Modeling a Proof-of-Concept

### 2021-11-13 paper/article.tex
Paper progress

@@

\subsubsection{Interleaved CPN/EN training, and adapting to non-stationarity}
Having defined the training epochs for the EN and CPN, we can define a training
algorithm on the basis of those two. We train the two in alteration, creating
a new EN each time we enter an EN training period. We explored the possibility
of reusing an existing EN by retraining it, for the purpose of training efficiency.
However, we found that retraining an EN was no more fast than training a new one,
and in-fact usually took longer, despite significant experimentation with learning
rates.

@@

@@

\section{Discussion and Conclusion}
\begin{itemize}
	\item Training efficiency
	\item Spectrum from simple low dimensional stimulation vectors today to higher dimensional future
	\item Toward in vivo application
\end{itemize}

>>>>

Clearly, training and deploying a neural co-processor in a true brain involves challenges we
don't capture with this simulation. We don't intend this simulation to constitute evidence
that our method will, for example, immediately translate to true restoration of fine-grained
control for individual fingers of a stroke patient. One clear challenge with doing so would be the
sheer dimensionality of natural brain dynamics, and how that compares to the resolution
of stimulation the co-processor can learn to apply. There exists a clear mismatch between
the dimensionality of the underlying problem, electrode technologies, and the amount of training
data which can reasonably be collected to train a closed-loop neural controller. We argue
that while this fact clearly creates a challenge for learning-based closed-loop stimulation,
that nevertheless the insights we are generating through this simulation are likely to be
applicable. As we show next, the simulation exhibits a number of properties that reflect
a real world application, which our co-processor design must contend with. In the Discussion
section below, we will explore how those insights are likely to lead to initial demonstrations
of the co-processor approach on lower dimensional problems.

@@

\subsubsection{Interleaved CPN/EN training, and adapting to non-stationarity}
Having defined the training epochs for the EN and CPN, we can define a training
algorithm on the basis of those two. We train the two in alternation, creating
a new EN each time we enter an EN training period. We explored the possibility
of reusing an existing EN by retraining it, for the purpose of training efficiency.
However, we found that retraining an EN was no more fast than training a new one,
and in-fact usually took longer, despite significant experimentation with learning
rates.

@@

TODO: talk about retraining more

@@

\section{Discussion and Conclusion}
\begin{itemize}
	\item Training efficiency
	\item Spectrum from simple low dimensional stimulation vectors today to higher dimensional future
	\item Toward in vivo application: example of lower dimensional problems this may help with
\end{itemize}
